---
title: "denen skal funke"
output: html_document
date: "2022-09-26"
editor_options: 
  chunk_output_type: console
---

<<<<<<< HEAD
```{r setup, echo=FALSE}



=======
```{r setup}
#| echo: false
#| warning: false
#| message: false
>>>>>>> 3cc4cde0bb6c2bdf857644f17382d4aa739d6ae7


library(readxl); library(tidyverse); library(gt)
lac_data <- read_excel("data/lac_data.xlsx", na = "NA")



lac_data %>%
  filter(time == "pre") %>%
  select(FP, sex, age, weight, height) %>%
  group_by(sex) %>%
  summarise(MeanAge = mean(age),
            sdAge = sprintf("(%.2f)", sd(age)),
            MeanHeight = mean(height),
            sdHeight = sprintf("(%.2f)", sd(height)),
            MeanWeight = mean(weight),
            sdWeight = sprintf("(%.2f)", sd(weight)), n = n()) %>%
  gt(caption = "Subjects") %>%
  cols_label(MeanAge = "Age",
             sdAge = "",
             MeanHeight = "Height",
             sdHeight = "",
             MeanWeight = "Weight",
             sdWeight = "",
             n = "Participants",
             sex = "Sex") 
```



```{r}
#| message: false
#| warning: false
#| echo: false


lac_data <- read_excel("data/lac_data.xlsx", na = "NA")


lac_data %>%
  select(FP, sex, time, watt_4mmol, HF_4mmol) %>%
  pivot_wider(names_from = time, 
              values_from = c(watt_4mmol, HF_4mmol)) %>%
  
  mutate(watt_diff = watt_4mmol_post - watt_4mmol_pre, 
         hf_diff = HF_4mmol_post - HF_4mmol_pre) %>%
  
  group_by(sex) %>%

  
  summarise(watt.s = sd(watt_diff, na.rm = TRUE), 
            hf.s = sd(hf_diff, na.rm = TRUE),
            watt.m = mean(c(watt_4mmol_pre, watt_4mmol_post), na.rm = TRUE), 
            hf.m = mean(c(HF_4mmol_pre, HF_4mmol_post), na.rm = TRUE), 
            watt.te = watt.s / sqrt(2), 
            hf.te = hf.s / sqrt(2), 
            watt.cv = 100 * (watt.te / watt.m), 
            hf.cv = 100 * (hf.te / hf.m), 
            n = n()) %>%
  
  print()



```





<<<<<<< HEAD
```{r}

```

=======
>>>>>>> 3cc4cde0bb6c2bdf857644f17382d4aa739d6ae7
